Assignment 5

### 2015-02-24 rmtw/a5/latex8.tex
Added more to related work

Good examples

Bad examples

What is the actual result, is it good or bad?

Why do they contradict, environment vs system?

@@

\SubSection{Notes4John}
\cite{volter2013model} says that MDSD will: increase development speed, increase quality, improve reusability, improved manageability through abstraction etc.

>>>>

Volter et al\cite{volter2013model} says that successful adoption of MDSD should increase development speed, increase software quality, improve reusability and improve manageability through abstraction.

Whittle and Hutchinson \cite{whittle2012mismatches} conducted a study whereby they examined 17 companies who were adopting MDSD. While they agreed that the successful adoption of MDSD can improve productivity through code generation, there are many pitfalls which can cause the adoption to fail. Whittle and Hutchinson found that in companies where the change was implemented bottom up, there was a higher degree of success. On the contrary to this, when change was top down, as suggested by academia and education, the adoption was often not as successful. A focus on Domain Specific Languages (DSLs) is what Whittle and Hutchinson suggest helps MDSD become successful in a company setting.

@@
